The Eternal Adversary between Censor and Circumvention

### 2024-12-02 paper/paper.tex
format fix
fix included tikz figures location
fix citation

\section{Related Work}
There are some existing works that discuss those technologies in specified aspects, such as TLS fingerprinting\cite{TLS_Fingerprinting}, active probing \cite{Active_Probing}, and analysis (or audition) of protocols \cite{shadowsocks_analysis} \cite{Trojan-Probe}. In this article, we intend to give an overview of these technologies with practical examples and real-world scenarios.

@@

\begin{figure}[!h]
\centering
\input{figures/mitm}
\caption{MITM attack: Attacker (M) intercepts messages between client (C) and server (S).}
\label{fig:mitm}
% \vspace{-0.2cm}
\end{figure}

@@

\begin{figure}[!h]
\centering
\input{figures/proxy}
\caption{Proxy-based network bypass: user (U) connects to server (S) through proxy (P), bypassing firewall restrictions (FW). Encrypted tunnel (Enc) prevents content inspection.}
\label{fig:proxy}
% \vspace{-0.2cm}
\end{figure}

@@

\begin{figure}[!h]
    \centering
    \input{figures/fallback}
    \caption{Fallback: Proxy servers filter (P) unauthentic incoming traffic (P) (Probes) and forward it to a real HTTP Server (F) and forward authentic traffic (C) to destination (D)}
    \label{fig:fallback}
\end{figure}

>>>>

\section{Related Work}
There are some existing works that discuss those technologies in specified aspects, such as TLS fingerprinting\cite{TLS_Fingerprinting}, active probing \cite{Active_Probing}, and analysis (or audition) of protocols \cite{shadowsocks_analysis} \cite{Trojan_Probe}. In this article, we intend to give an overview of these technologies with practical examples and real-world scenarios.

@@

\begin{figure}[!h]
\centering
\input{include/mitm}
\caption{MITM attack: Attacker (M) intercepts messages between client (C) and server (S).}
\label{fig:mitm}
% \vspace{-0.2cm}
\end{figure}

@@

\begin{figure}[!h]
\centering
\input{include/proxy}
\caption{Proxy-based network bypass: user (U) connects to server (S) through proxy (P), bypassing firewall restrictions (FW). Encrypted tunnel (Enc) prevents content inspection.}
\label{fig:proxy}
% \vspace{-0.2cm}
\end{figure}

@@

\begin{figure}[!h]
    \centering
    \input{include/fallback}
    \caption{Fallback: Proxy servers filter (P) unauthentic incoming traffic (P) (Probes) and forward it to a real HTTP Server (F) and forward authentic traffic (C) to destination (D)}
    \label{fig:fallback}
\end{figure}
